Global patterns of forest autotrophic carbon fluxes

### 2021-02-23 manuscript/manuscript draft.Rmd
Update manuscript draft.Rmd
issue #128 clarified seasonality discussion slightly

Forest C fluxes decline with temperature seasonality (Table 1, *Q4*; Fig. 4e), as is to be expected given that fluxes are minimal during winters. 
A temperature-defined growing season length correlated with global-scale variation in annual C flux [Table 1, *Q5*; Fig. 4f; see also @churkina_spatial_2005], consistent with the idea that the latitudinal gradient in carbon flux is attributable more to shorter growing seasons at high latitudes than to inherently lower rates of photosynthesis or respiration by high-latitude forests [@enquist_adaptive_2007; @fu_maximum_2019]. 
While there is evidence that trees in high-latitude forests have adaptations to maximize photosynthesis at low temperatures [@helliker_subtropical_2008; @huang_air_2019], this is not sufficient to yield growing season fluxes comparable to those of tropical forests, as indicated by a number of positive correlations between monthly mean flux during the growing season and growing season temperature, solar radiation, and $PET$ (Table 1, Figs. S8-S9).
Thus, we reject the hypothesis that growing season length alone accounts for global-scale variation in productivity--*i.e.*, that there is no relationship between C flux per month of the growing season and growing season climatic conditions [Table 1, *Q5*; @kerkhoff_plant_2005; @enquist_adaptive_2007; @michaletz_convergence_2014]. 
Rather, annual C flux is shaped by both growing season length and the climate of peak growing season months [@chu_does_2016; @fu_maximum_2019]. 
Given strong co-variation between growing season length and $MAT$ [Fig. S2; @chu_does_2016], accurately partitioning this variation will require data on intra-annual variation in C flux coupled with a higher-precision metric of growing season length than the monthly-resolution metric used here [e.g., based on leaf phenology or C exchange, *sensu* @fu_maximum_2019]. 
@fu_maximum_2019 find that global-scale geographic variation in annual $NEE$ is driven more strongly by growing season length than by carbon uptake rates within the growing season, whereas interannual variation in $NEE$ and $GPP$ at any given site appears to be driven predominantly by the maximum rate of C uptake, as opposed to growing season length [@zhou_explaining_2016; @fu_maximum_2019; @zani_increased_2020].
Further analysis of interannual variation in C fluxes in relation to climate will be valuable to disentangling how seasonality shapes broad geographic patterns in forest C flux.

>>>>

Forest C fluxes decline with temperature seasonality (Table 1, *Q4*; Fig. 4e), as is to be expected given that fluxes are minimal during winters. 
A temperature-defined growing season length correlated with global-scale variation in annual C flux [Table 1, *Q5*; Fig. 4f; see also @churkina_spatial_2005], consistent with the idea that the latitudinal gradient in carbon flux is attributable more to shorter growing seasons at high latitudes than to inherently lower rates of photosynthesis or respiration by high-latitude forests [@enquist_adaptive_2007; @fu_maximum_2019]. 
However, we find evidence that, within the growing season, climate still plays an important role in shaping C fluxes, as indicated by a number of positive correlations between monthly mean flux during the growing season and growing season temperature, solar radiation, and $PET$ (Table 1, Figs. S8-S9). This suggests that, while trees in high-latitude forests have adaptations to maximize photosynthesis at low temperatures [@helliker_subtropical_2008; @huang_air_2019], this is not sufficient to yield growing season fluxes comparable to those of tropical forests.
Thus, we reject the hypothesis that there is no relationship between C flux per month of the growing season and growing season climatic conditions [Table 1, *Q5*; @kerkhoff_plant_2005; @enquist_adaptive_2007; @michaletz_convergence_2014]: growing season length alone is insufficient to account for global-scale variation in productivity. 
Rather, annual C flux is shaped by both growing season length and the climate of peak growing season months [@chu_does_2016; @fu_maximum_2019]. 
Given strong co-variation between growing season length and $MAT$ [Fig. S2; @chu_does_2016], accurately partitioning this variation will require data on intra-annual variation in C flux coupled with a higher-precision metric of growing season length than the monthly-resolution metric used here [e.g., based on leaf phenology or C exchange, *sensu* @fu_maximum_2019]. 
@fu_maximum_2019 find that global-scale geographic variation in annual $NEE$ is driven more strongly by growing season length than by carbon uptake rates within the growing season, whereas interannual variation in $NEE$ and $GPP$ at any given site appears to be driven predominantly by the maximum rate of C uptake, as opposed to growing season length [@zhou_explaining_2016; @fu_maximum_2019; @zani_increased_2020].
Further analysis of interannual variation in C fluxes in relation to climate will be valuable in disentangling how seasonality shapes broad geographic patterns in forest C flux.
